The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women

### 2025-03-30 products/manuscript/Manuscript.qmd
update

---
title: "The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women"
author: "Asmith Joseph"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Load required packages
library(tibble)
library(knitr)
library(kableExtra)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Load required packages
library(ggplot2)

>>>>

---
title: "The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women"
author: "Asmith Joseph"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
output-dir: "C:/Users/ajose35/Desktop/MADA-course/Joseph-MADA-project/products/manuscript"
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Code that generates HTML widget or output

# Load required packages
library(tibble)
library(knitr)
library(kableExtra)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Code that generates HTML widget or output

# Load required packages
library(ggplot2)
